\documentclass{article}


\PassOptionsToPackage{numbers, compress}{natbib}

\newcommand{\haotian}[1]{{\color{red}{#1}}}


\usepackage[preprint]{neurips_2024}






\usepackage[utf8]{inputenc} %
\usepackage[T1]{fontenc}    %
\usepackage{hyperref}       %
\usepackage{url}            %
\usepackage{booktabs}       %
\usepackage{amsfonts}       %
\usepackage{mathtools} %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage{xcolor}         %
\usepackage{listings}

\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{graphbox}
\usepackage{amssymb} %
\usepackage{pifont}  %
\usepackage[inline]{enumitem}
\usepackage{wrapfig}
\usepackage{booktabs} %
\usepackage{array}    %
\usepackage{float} %

\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\tiny\ttfamily,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\definecolor{darkred}{rgb}{0.6, 0.0, 0.0}  %
\definecolor{Blue}{rgb}{0.2,0.2,0.6}
\hypersetup{
  colorlinks=true,
  citecolor=Blue,
  linkcolor=Blue,
  urlcolor=Blue,
}%
\usepackage{tikz} %
\usetikzlibrary{fit,positioning,arrows,automata}

\usepackage{cleveref}
\crefname{figure}{Fig.}{Figs.}
\Crefname{figure}{Fig.}{Figs.}
\crefname{section}{Sec.}{Sec.}
\Crefname{section}{Sec.}{Sec.}
\crefname{table}{Table}{Table}
\Crefname{table}{Table}{Table}
\crefname{listing}{Listing}{Listing}

\newcommand{\cmark}{\textcolor{green}{\ding{51}}} %
\newcommand{\xmark}{\textcolor{red}{\ding{55}}}   %
\newcommand{\ours}{\texttt{RefDrop}}
\newcommand{\cliche}{\text{cliché }}
\newcommand{\rma}{\texttt{RFG}}
\newcommand{\RMA}{\text{Reference Feature Guidance}}

\newcommand{\mR}{{\mathbb R}}
\def\<{{\langle}}
\def\>{{\rangle}}

\newcommand{\fan}[1]{\textcolor{violet}{#1}}
\newcommand{\chen}[1]{\textcolor{cyan}{#1}}
\newcommand{\qsh}[1]{\textcolor{blue}{#1}}

\title{RefDrop: Controllable Consistency in Image or Video Generation via Reference Feature Guidance}




\author{%
  Jiaojiao Fan
    \\
  Georgia Tech\\
  \texttt{sbyebss@gmail.com} \\
  \And
  Haotian Xue \\
  Georgia Tech \\
  \texttt{htxue.ai@gatech.edu} \\
  \AND
  Qinsheng Zhang\thanks{Work done while the author was in Georgia Tech.}  \\
  NVIDIA \\
  \texttt{qsh.zh27@gmail.com} \\
  \And
  Yongxin Chen \\
  Georgia Tech \\
  \texttt{yongchen@gatech.edu} \\
}


\begin{document}


\maketitle



\input{main.tex}
\input{supple.tex}


\end{document}
